Data Cleaning

### 2025-12-09 Data Cleaning.Rmd
Added a single line to test pulling.
Attempted to pull previous year doses as a predictor.

df_lag_incdec <- df_lag_incdec |> 
  mutate(Timestamp = ymd(df_lag_incdec$Timestamp))

@@

>>>>

df_lag_incdec <- df_lag_incdec |> 
  mutate(Timestamp = ymd(Timestamp))

@@

```{r}
# Look at performance of a model that simply pulls previous year dose

dosing <- read_csv("CoagulantDoses_2017-20.csv")
dosing <- dosing |> 
  mutate(Timestamp = mdy(dosing$Date)) |>
  select(-c(Date))

df_lag_incdec_prevdose <- df_lag_incdec |>
  rowwise() |>
  mutate(
    target_time = Timestamp - years(1),
    FeCl_prev = dosing$Ferric.chloride..mg.L[which.min(abs(dosing$Timestamp - target_time))],
    Polymer_prev = dosing$`Cationic Polimer, mg/L`[which.min(abs(dosing$Timestamp - target_time))]) |>
  ungroup()

```{r}
df_lag_incdec |>
  rename(FeCl_dose = Ferric.chloride..mg.L,
         Polymer_dose = Cationic.Polimer..mg.L)

write.csv(df_lag_incdec, "RWAR_dosing_lag_incdec.csv")
